Coalition Formation Algorithm of Prosumers in a Smart Grid Environment

### 2014-09-26 Article.tex
new version of utility plot

@@

\begin{table}[!t]
\centering
\scriptsize
\begin{tabular}{l|p{4.5cm}}
  \hline 
  \\
  $ \mathcal{A}=\{a_{1},...,a_{N}\} $ & Set of agents \\
  $ P_{i}(t) \in \mathbb{R}\ \ (P_{s}(t)) $ & Instantaneous production of agent $i$ at time $t$ \\
  $ \mathcal{T}_{i} = \{P_{i}(t_{0}),...,P_{i}(t_{K})\} $ & Time series of agent i available production values \\
  $ \mathcal{F}(P_{i})\ \ (\mathcal{F}(P_{S})) $ & Probability distribution of the production of the agent $i$ \\
  $ \phi \in [0,1] $ & Reliability threshold \\
  $ P^{MIN} \in \mathbb{R}^+ $ & Min value threshold \\
  $ P_{s}^{CRCT} \in \mathbb{R}^+ $ & Contract value of coalition s \\
  $ P_{\phi}(s) \in \mathbb{R}^+ $ & Max contract value under $ \phi $ constraint \\
  $ \mathcal{U}_{\phi,\ P^{MIN}}(s) $ & Utility function \\
  $ \tau_{i}(s) \in \mathbb{R}$ & Decision rule for mapping overlapping into disjoint coalitions \\
  $ \epsilon \in [0,1] $ & Pruning threshold for the correlation graph \\
  $ N_{COAL} \in \mathbb{Z}^+ $ & Number of desired coalition \\
  $ CS $ & Set of all coalition structures \\
  $ \Theta(G) $ & Set of non overlaping cliques in graph G \\
  \\
  \hline
\end{tabular}

@@

\begin{figure}
 \centering
  \subcaptionbox{$ (\phi, P^{MIN}) $ subspace\label{fig2:a}}{\includegraphics[width=1.7in]{./figure1/util}}
  \subcaptionbox{$ (N_{COAL}, P^{MIN}) $ subspace\label{fig2:b}}{\includegraphics[width=1.70in]{./figure6/util2}}
\caption{Utility function as function of the parameters space $\{\phi \in [0,1], N_{COAL}\in \mathbb{Z}^+, P^{MIN} \in \mathbb{R}^+\}$: In $ \{\phi \in [0,0.6], P^{MIN}\} $ when $ N_{COAL} $ is fixed (fig \ref{fig2:a}), and in $ \{N_{COAL}, P^{MIN}\} $ for a fixed $ \phi $ (fig \ref{fig2:b}). For readability, $ P^{MIN} $ is expressed in tenth of MW.}
\label{Fig2}
\end{figure}

As shown in figure \ref{fig2:a}, the parameters $\phi$ and $P^{MIN}$ shape the utility function such that, if $ \phi $ is close to zero, the reliability requirement is very high. Only small values of $ P^{MIN}$ could then potentially lead to valid coalitions (and positive utilities). Conversely, the higher $\phi$, the less constraints are imposed to the coalitions and more valid coalitions can arise for a larger spectrum of $ P^{MIN}$. Obviously, the highest utility values are found for high $ \phi $, because the coalitions formed are able to announce higher contract values, yielding higher utilities.

In figure \ref{fig2:b}, we fix the reliability to a given empirical value ($\phi = 0.08 $). We can observe how the social welfare $\sum_{s \in S} \mathcal{U}_{\phi,\ P^{MIN}}(s)$ evolves according to $P^{MIN}$ and $ N_{COAL} $. In our setting we notice a maximum point around $ N_{COAL} = 3 $, followed by a decrease. There is clearly a maximum number of coalitions sustainable for a given set of parameters. After this value we will form more coalitions that would be unable to pass the grid requirements. Moreover, reckon that increasing $ N_{COAL} $ means also increasing $ \epsilon $, leading to denser graphs, meaning that the algorithm performance will also decrease.

>>>>

\begin{table}[t]
\centering
\scriptsize
\begin{tabular}{l|p{4.5cm}}
  \hline 
  \\
  $ \mathcal{A}=\{a_{1},...,a_{N}\} $ & Set of agents \\
  $ P_{i}(t) \in \mathbb{R}\ \ (P_{s}(t)) $ & Instantaneous production of agent $i$ at time $t$ \\
  $ \mathcal{T}_{i} = \{P_{i}(t_{0}),...,P_{i}(t_{K})\} $ & Time series of agent i available production values \\
  $ \mathcal{F}(P_{i})\ \ (\mathcal{F}(P_{S})) $ & Probability distribution of the production of the agent $i$ \\
  $ \phi \in [0,1] $ & Reliability threshold \\
  $ P^{MIN} \in \mathbb{R}^+ $ & Min value threshold \\
  $ P_{s}^{CRCT} \in \mathbb{R}^+ $ & Contract value of coalition s \\
  $ P_{\phi}(s) \in \mathbb{R}^+ $ & Max contract value under $ \phi $ constraint \\
  $ \mathcal{U}_{\phi,\ P^{MIN}}(s) $ & Utility function \\
  $ \tau_{i}(s) \in \mathbb{R}$ & Decision rule for mapping overlapping into disjoint coalitions \\
  $ \epsilon \in [0,1] $ & Pruning threshold for the correlation graph \\
  $ N_{COAL} \in \mathbb{Z}^+ $ & Number of desired coalition \\
  $ CS $ & Set of all coalition structures \\
  $ \Theta(G) $ & Set of non overlaping cliques in graph G \\
  \\
  \hline
\end{tabular}

@@

@@

\begin{figure}
 \centering
  \includegraphics[scale=0.9]{./figure9/util}
\caption{Utility function as function of the parameters space $\{\phi \in [0,1], N_{COAL}\in \mathbb{Z}^+, P^{MIN} \in \mathbb{R}^+\}$: a) In $ \{\phi \in [0,0.6], P^{MIN}\} $ when $ N_{COAL} $ is fixed. b) in $ \{N_{COAL}, P^{MIN}\} $ for a fixed $ \phi $. For readability, $ P^{MIN} $ is expressed in tenth of MW.}
\label{Fig2}
\end{figure}

As shown in figure \ref{Fig2}a, the parameters $\phi$ and $P^{MIN}$ shape the utility function such that, if $ \phi $ is close to zero, the reliability requirement is very high. Only small values of $ P^{MIN}$ could then potentially lead to valid coalitions (and positive utilities). Conversely, the higher $\phi$, the less constraints are imposed to the coalitions and more valid coalitions can arise for a larger spectrum of $ P^{MIN}$. Obviously, the highest utility values are found for high $ \phi $, because the coalitions formed are able to announce higher contract values, yielding higher utilities.

In figure \ref{Fig2}b, we fix the reliability to a given empirical value ($\phi = 0.08 $). We can observe how the social welfare $\sum_{s \in S} \mathcal{U}_{\phi,\ P^{MIN}}(s)$ evolves according to $P^{MIN}$ and $ N_{COAL} $. In our setting we notice a maximum point around $ N_{COAL} = 3 $, followed by a decrease. There is clearly a maximum number of coalitions sustainable for a given set of parameters. After this value we will form more coalitions that would be unable to pass the grid requirements. Moreover, reckon that increasing $ N_{COAL} $ means also increasing $ \epsilon $, leading to denser graphs, meaning that the algorithm performance will also decrease.
